Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-03-05 paper/main.tex
Finished drafting GPU parallelism section

The GPU executes programs as SIMT (Single Instruction Multiple Threads) in
groups of 32 threads called \emph{warps}.  These warps are then grouped into
higher levels called \emph{thread blocks} and \emph{grids}.  It is impossible
to communicate between SMPs during gpu program execution, computational tasks
are typically broken up into multiple gpu programs (kernels) that are executed
serially.

@@

@@

% DREW Idea... in hindsight, maybe we should still try many kernel launches. 
% instances can still exit early, and can still update a global variable signaling
% that they're done

%even if it
% means individual instances can't terminate early.

>>>>

The GPU executes programs as SIMT (Single Instruction Multiple Threads) in
groups of 32 threads called \emph{warps}.  These warps are then grouped into
higher levels called \emph{thread blocks} and \emph{grids}.  It is impossible
to communicate between SMPs during gpu program execution, so computational tasks
are typically broken up into multiple gpu programs (kernels) that are executed
serially.

@@

One possible implementation of the iterative alignment stage would be to
perform the optimization for all instances simultaneously, but to perform each
linear algebraic operation in a separate gpu kernel call.  The primary
advantage of this implementation strategy is that every kernel would be
performing a very simple operation requiring fewer registers per thread.  The
registers in a GPU are shared between all executing threads thus, barring other
hardware limitations, the fewer registers each thread requires, the more
threads can be scheduled to run simultaneously.  The primary downside of this
approach is that it forces synchronization between all problem instances.  It will
also have increased kernel launch overhead and potentially less efficient use of
the GPU's L2 cache.
% DREW Idea... in hindsight, maybe we should still try many kernel launches. 
% instances can still exit early, and can still update a global variable signaling
% that they're done

@@

The full resolution test image, along with its numerical derivatives in both
image directions, are stored in GPU texture memory. This  allows the
recomputation of $b(\tau)$ and $J(\tau)$, which essentially consist of warped
versions of the test image and its derivatives, to exploit the GPU's special
purpose hardware for bilinear interpolation.
